---
title: 'Assignment A01: GGPLOT2 '
author: Nouran
date: '2021-05-22'
slug: assignment-a01-ggplot2
categories:
  - ggplot2
tags: []
---



## First, The Effect of Vitamin C on Tooth Growth in Guinea Pigs

In this blog we are going to show the effect of providing vitamin C on the growth of the odontoblasts of 60 guinea pigs.

#### Keywords:

* Odontoblasts: cells responsible for tooth growth
* Ascorbic acid: a form of vitamin C and coded as VC.


#### Each pig received one of three dose levels of vitamin C which are:

a. 0.5 mg/day
b. 1   mg/day
c. 2   mg/day 


#### The Vitamin C dose is provided by one of the two following delivery methods:

1. Through orange juice.
2. Through ascorbic acid.

The collected data is composed of 60 observations one for each pig where the tooth length, taken dose and the delivery method are recorded.


### The number of participant in each dose level providing the dose delivery method

```{r,message=FALSE,echo=FALSE,warning=FALSE}
library(ggplot2)
ggplot(ToothGrowth,aes(x=dose,fill=supp))+
  theme(axis.ticks.x=element_blank(), axis.text.x =element_blank() )+
  geom_bar(position = "dodge")+
  labs(title="Number of participants in each dose level for each delivery method ",x="Dose Level", fill="Delivery Method", subtitle = "", 
        caption = "Fig (1)                                                                               ")+
  facet_wrap(~ dose)
```
from the above Fig (1), we can see that for every dose level there are 20 participants and from which 10 participants received the dose through orange juice (OJ) and the other 10 participants received the dose through ascorbic acid (VC).


### The relationship between the tooth growth and the dose level



```{r,message=FALSE,echo=FALSE,warning=FALSE}
ggplot(ToothGrowth, aes(len,dose,shape=supp,color=supp)) + 
  geom_point(shape=1) +
  labs(title="           Tooth Growth Vs Dose Level for each Delivery Method",x="Tooth Length",y="Dose",
       caption = "Fig(2)                                                                                       ")

```
From Fig(2) we can see that the tooth growth that is determined by measuring the tooth length vs the dose level given to each pig providing the delivery method of the dose. 


### Grouping the data based on both the dose and the delivery method
```{r,message=FALSE,echo=FALSE,warning=FALSE}
ggplot(ToothGrowth,aes(x=dose,y=len,color=supp))+
  geom_point(shape=1,position="jitter")+
  labs(title="                               Tooth growth under each group",x="Dose Level",y="Tooth Length", caption="Fig(3)                                                                                               ")+
  facet_wrap(supp~dose)+
    theme(axis.ticks.x=element_blank(), axis.text.x =element_blank() )

```
From Fig(3), we can have a more detailed information about each group, where the grouping is done based on the dose level and the dose delivery method. in fig (3), we can see that the group with dose level equal 2 mg/day and deliver the dose through ascorbic acid (VC/2) achieved the largest tooth growth but when the dose was 0.5 mg/day and the delivery method was VC, it achieved the lowest tooth growth.

### Distribution of Tooth growth at each dose level for each delivery method

```{r,message=FALSE,echo=FALSE,warning=FALSE}
library(ggridges)
ggplot(ToothGrowth, aes(x = len, y = as.factor(dose), fill = supp)) + 
  geom_density_ridges(alpha = 0.5)+
labs(title="Distribution of Tooth growth at each dose level for each delivery method ",x="Tooth Length",
 y="Dose level",caption = "Fig(4)                                                                                                ")
```
From Fig (4), we can see that at dose level 0.5 and 1 mg/day the tooth growth is better when the delivery method is the orange juice and at dose level of 2mg/day the tooth growth is better when the dose is delivered by ascorbic acid.
 
 
### Tooth length histogram

```{r}
ggplot(ToothGrowth,aes(x=len))+
geom_histogram(binwidth = 1)+
labs(title="                                Counts for Tooth length measurements ",x="Tooth Length",
 caption = "Fig(5)                                                                                                       ")
```
From Fig(5), we can see that the peak of the histogram occurs at length around 26 with 5 teeth occurred at the bin.


### Density of the tooth growth based on the dose delivery method
```{r,message=FALSE,echo=FALSE,warning=FALSE}
library(ggridges)
ggplot(ToothGrowth,aes(x=len,fill=supp))+
geom_density(alpha=0.5)+
  labs(title="                Tooth growth based on the Delivery method",x="Tooth Length",y="Density",fill="Delivery Method", caption = "Fig(6)                                                                                    ")
 


```
Fig (6), shows the distribution of tooth length for each dose delivery method.

### Boxplot for the tooth length distribution based on the delivery method

```{r,message=FALSE,echo=FALSE,warning=FALSE}
ggplot(ToothGrowth, aes(x = supp, y = len)) + geom_boxplot(aes(fill = supp))+
  labs(title="           Tooth growth based on the dose delivery method",x="Delivery Method",y="Length",fill="Delivery Method", caption = "Fig(7)                                                                                    ")
```

Fig(7) shows the distribution of the tooth growth data based on each dose delivery method. This boxplot shows the minimum, maximum, median, first quartile and third quartile in the data set.


### Density of the tooth growth based on the dose level
```{r,message=FALSE,echo=FALSE,warning=FALSE}
library(ggridges)
ToothGrowth$dose <- as.factor(ToothGrowth$dose)
ggplot(ToothGrowth,aes(x=len, fill=dose)) + geom_density(alpha=0.3)+
  labs(title="                Tooth growth based on the Dose level",x="Tooth Length",y="Density",fill="Dose  Level ",caption = "Fig(8)                                                                                      ")
 
```

Fig (8), shows the distribution of tooth length for each dose level.

### Boxplot for the tooth length distribution based on the dose level

```{r,message=FALSE,echo=FALSE,warning=FALSE}
ggplot(ToothGrowth, aes(x = supp, y = len)) + geom_boxplot(aes(fill = dose))+
  labs(title="                        Tooth growth based on the dose level",x="Dose Level",y="Length",fill="Dose Level", caption = "Fig(9)                                                                                    ")
```


Fig (9), shows the distribution of the tooth growth data based on each dose level. This boxplot shows the minimum, maximum, median, first quartile and third quartile in the data set.

## Second, Average Heights and Weights for American Women


This data set provides the average heights and weights for American women of age ranges from 30 to 39

```{r}
ggplot(women,aes(height,weight))+geom_point()+labs(title="                                                  Height vs weight",x="Height in In ",y="Weight in Ibs", caption = "Fig(10)                                                                                                       ")

```

Fig (10), shows us that the relationship between the height and the weight for the American women is linearly.



