---
title: 'A01 Linear Regression '
author: Nouran
date: '2021-07-09'
slug: a01-linear-regression
categories:
  - Basics
  - ggplot2
  - shiny
  - Tideverse
  - tidymodels
tags: []
---

```{r}
library("readxl")
library("DataExplorer")
library("janitor")
library("tidyr")
```

## The diamond ring data 

In this blog we used the diamond ring data. Getting a glimpse into the data we can see that it is composed of 440 rows where each row represents a diamond ring and for each ring the diamond characteristics are provided that are Color, Cut, Carat Weight, Clarity , Polish, Symmetry, and certification in addition to the price.

```{r,warning=FALSE}
data<-read_excel("diamonds.xlsx",col_types = c("guess","guess","guess","guess","guess","guess","guess","numeric","guess"))%>%
  clean_names()
 glimpse(data)

```


## The Univriate Analysis

we will start our analysis with the metric data which are the price and the carat mass of the daimond ring


### The Price
```{r}

### The histogram of the price :
ggplot(data,aes(price))+
  geom_histogram()+
  labs(
    title = "Histogram of the Price",
    subtitle = " ",
    x = "Price"
  )+
 theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
    theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
      theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))



### The boxplot of the price 
ggplot(data,aes(price))+
  geom_boxplot()+
  labs(
    title = "The Price ",
    subtitle = " ",
    x = "Price"
  )+
 theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
    theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
      theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))

### summary of the price o get the min, max, Q1,Q3, mean and median 
 summary(data$price)

### The variance and standard deviation of the price 
var(data$price)
sd(data$price)

### The mode of the price 
mode_price<- data %>%
  count(price)%>%
  arrange(desc(n))%>%
  head(1)


### The IQR of the price 
iqr_price=quantile(data$price, 0.75) - quantile(data$price, 0.25)


```


### The Carat mass

```{r}

### The histogram of the Carat :
ggplot(data,aes(carat))+
  geom_histogram()+
  labs(
    title = "Histogram of the Carat",
    subtitle = " ",
    x = "The Carat Mass"
  )+
 theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
    theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
      theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))



### The boxplot of the carat 
ggplot(data,aes(carat))+
  geom_boxplot()+
  labs(
    title = "The Carat Mass ",
    subtitle = " ",
    x = "Carat Mass"
  )+
 theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
    theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
      theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))

### summary of the carat mass to get the min, max, Q1,Q3, mean and median 
 summary(data$carat)

### The variance and standard deviation of the carat mass 
var(data$carat)
sd(data$carat)

### The mode of the carat mass 
mode_carat<- data %>%
  count(carat)%>%
  arrange(desc(n))%>%
  head(1)


### The IQR of the carat mass
iqr_carat=quantile(data$carat, 0.75) - quantile(data$carat, 0.25)


```



### The Colour

```{r}

ggplot(data,aes(colour))+
  geom_bar()+
  labs(
    title = "Histogram of the Colour",
    subtitle = " ",
    x = "Colour"
  )+
 theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
    theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
      theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))
```


###  The Clarity
```{r}

ggplot(data,aes(clarity))+
  geom_bar()+
  labs(
    title = "Histogram of the Clarity",
    subtitle = " ",
    x = "Clarity"
  )+
 theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
    theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
      theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))
```


### The Cut
```{r}

ggplot(data,aes(cut))+
  geom_bar()+
  labs(
    title = "Histogram of the Cut",
    subtitle = " ",
    x = "Cut"
  )+
 theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
    theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
      theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))

```


### The Certification
```{r}

ggplot(data,aes(certification))+
  geom_bar()+
  labs(
    title = "Histogram of the Certification",
    subtitle = " ",
    x = "Certification"
  )+
 theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
    theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
      theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))


```



### The Polish
```{r}


ggplot(data,aes(polish))+
  geom_bar()+
  labs(
    title = "Histogram of the Polish",
    subtitle = " ",
    x = "polish"
  )+
 theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
    theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
      theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))


```


### The Symmetry

```{r}


ggplot(data,aes(symmetry))+
  geom_bar()+
  labs(
    title = "Histogram of the Symmetry",
    subtitle = " ",
    x = "Symmetry"
  )+
 theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
    theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
      theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))


```


### Wholesaler

```{r}

ggplot(data,aes(wholesaler))+
  geom_bar()+
  labs(
    title = "Histogram of the Wholesaler",
    subtitle = " ",
    x = "Wholesaler"
  )+
 theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
    theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
      theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))


```


## The Bivariate Analysis


### The price and the carat mass 

```{r}

ggplot(data,aes(carat,price))+
  geom_boxplot()+
  labs(
    title = "Price Vs. Carat",
    subtitle = " ",
    y= " price ",
    x = "Carat"
  )+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
  theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))

cor (data$carat,data$price)
cov(data$carat,data$price)
```

### The price and the colour 

```{r}
ggplot(data,aes(colour,price))+
  geom_boxplot()+
  labs(
    title = "Price Vs. Colour",
    subtitle = " ",
    y= " price ",
    x = "Colour"
  )+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
  theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))


# Compute the analysis of variance through Anova 
res.aov_colour <- aov(price ~ colour, data = data)
# Summary of the analysis
summary(res.aov_colour)
```


### The price and the clarity 

```{r}
ggplot(data,aes(clarity,price))+
  geom_boxplot()+
  labs(
    title = "Price Vs. Clarity",
    subtitle = " ",
    y= " price ",
    x = "Clarity"
  )+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
  theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))


# Compute the analysis of variance through Anova 
res.aov_clarity <- aov(price ~ clarity, data = data)
# Summary of the analysis
summary(res.aov_clarity)
```
### The price and the cut 

```{r}

ggplot(data,aes(cut,price))+
  geom_boxplot()+
  labs(
    title = "Price Vs. Cut",
    subtitle = " ",
    y= " price ",
    x = "Cut"
  )+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
  theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))

# Compute the analysis of variance through Anova 
res.aov_cut<- aov(price ~ cut, data = data)
# Summary of the analysis
summary(res.aov_cut)
```


### The price and the certification 

```{r}

ggplot(data,aes(certification,price))+
  geom_boxplot()+
  labs(
    title = "Price Vs. Certification",
    subtitle = " ",
    y= " price ",
    x = "Certification"
  )+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
  theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))


# Compute the analysis of variance through Anova 
res.aov_certification <- aov(price ~ certification, data = data)
# Summary of the analysis
summary(res.aov_certification)
```

### The price and the polish 

```{r}

ggplot(data,aes(polish,price))+
  geom_boxplot()+
  labs(
    title = "Price Vs. Polish",
    subtitle = " ",
    y= " price",
    x = "Polish"
  )+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
  theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))


# Compute the analysis of variance through Anova 
res.aov_polish <- aov(price ~ polish, data = data)
# Summary of the analysis
summary(res.aov_polish)
```

### The price and the symmetry 

```{r}

ggplot(data,aes(symmetry,price))+
  geom_boxplot()+
  labs(
    title = "Price Vs. Symmetry",
    subtitle = " ",
    y= " price ",
    x = "Symmetry"
  )+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
  theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))

# Compute the analysis of variance through Anova 
res.aov_symmetry <- aov(price ~ symmetry, data = data)
# Summary of the analysis
summary(res.aov_symmetry)
```

### The price and the wholesaler

```{r}

ggplot(data,aes(wholesaler,price))+
  geom_point()+
  labs(
    title = "Price Vs. Wholesaler",
    subtitle = " ",
    y= " price ",
    x = "Wholesaler"
  )+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
  theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))

# Compute the analysis of variance through Anova 
res.aov_wholesaler <- aov(price ~ wholesaler, data = data)
# Summary of the analysis
summary(res.aov_wholesaler)
```


## The Regression Model 




### The simple regression model for the price Vs. the carat mass

```{r}
ggplot(data,aes(carat,price))+
  geom_point()+
  geom_smooth(method="lm", se=FALSE)+
  labs(
    title = "Fitting Linear Model for the Price Vs. Carat Mass",
    subtitle = " ",
    y= " price ",
    x = "Carat Mass"
  )+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme_bw()+
  theme(axis.text.x=element_text(color = "red", size=9, vjust=.5, hjust=0.7)) +
  theme(plot.background = element_rect(fill = "#BFD5E3"))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.title = element_text(hjust = 0.5))+
  theme(plot.caption  = element_text(hjust = 0.5),plot.subtitle = element_text(hjust = 0.5))+
  theme(plot.subtitle = element_text(colour = "#E48957", face = "bold", size = rel(1.5)))
  
  lm(price ~ carat, data = data)

```

### The simple regression model for the price Vs. the colour 


```{r}

lm(price ~ colour, data = data)
```


###  The simple regression model for the price Vs. clarity
```{r}

lm(price ~ clarity, data = data)
```


### The simple regression model for the price Vs. cut
```{r}

lm(price ~ cut, data = data)
```


### The simple regression model for the price Vs. the certification
```{r}

lm(price ~ certification, data = data)
```



### The simple regression model for the price Vs. the polish
```{r}

lm(price ~ polish, data = data)
```



### The simple regression model for the price Vs. the symmetry
```{r}

lm(price ~ symmetry, data = data)
```


### The simple regression model for the price Vs. the wholsaler
```{r}

lm(price ~ factor(wholesaler), data = data)
```
### The multiple linear regression:

```{r}

lm(price ~ carat+ colour+ clarity + cut+ certification + polish + symmetry +factor(wholesaler), data = data)
```
